Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-08 CVPR16/Source/contBBoxModel.tex
Camera ready version

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is usually not desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of our proposed detection bounding box is known to be
occluded, we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundaries of the detection bounding box, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in the detection score is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix as follows
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

The energy of detection scores is simply taken to be the inverse of the detection score as
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align}

>>>>

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is usually not desirable to use a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
\label{eq:GMMscores}
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we 
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of the proposed detection bounding box is known to be 
occluded, one would like to decrease the confidence in the detection score 
about the localization of that end of the object. Assuming that occlusions 
are more likely on the boundaries of the detection bounding box, we wish to decrease the 
confidence on the mean detection boundaries around the occluded boundaries.
To re-model detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ in \eqref{eq:GMMscores} and augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$, where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix for the detection scores is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix, as follows:
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

The energy of detection scores is simply taken to be the inverse of the above detection score, that is,
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align}

### 2016-04-08 CVPR16/Source/discussions.tex
Camera ready version

We have presented a theoretically novel continuous model for occlusion reasoning in 3D. A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores. We demonstrate unified modeling for different applications such as point tracks associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference. Another direction for future work is to replace a single ellipsoid by a set of spheres for modelling a translucent object~\cite{Rhodin2015}, which will better capture object boundary and appearance while remaining a continuous model.

>>>>

We have presented a theoretically novel continuous model for occlusion reasoning in 3D. A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores. We demonstrate unified modeling for different applications such as object-point track associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for object-point association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, which will allow belief propagation for fast inference. Another direction for future work is to replace a single ellipsoid by a set of spheres for modelling a translucent object~\cite{Rhodin2015}, which will better capture object boundary and appearance while remaining a continuous model.

\vspace{-0.2cm}
\paragraph{Acknowledgments}
This work was part of V.~Dhiman's internship at NEC Labs America, in Cupertino. V.~Dhiman and J.~J.~Corso were also supported by NSF NRI IIS 1522904.

### 2016-04-08 CVPR16/Source/experiments2.tex
Update ordering in Figure 6
Parameter settings, Cite related work by Reviewer 2
Camera ready version

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010}. We then show how the proposed model may be applied for 3D object localization in road scenes. For our experiments, we use 35 sequences of the KITTI raw dataset~\cite{Geiger_etal_2012}, which are recorded under a variety of driving conditions and include 10,088 frames and 634 object tracks in total. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\begin{figure*}[!!t]
\centering
%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{\small Association errors on different sets of input point tracks. Numbers on x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

@@

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Errors & Associations & Errors\\
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The ``Errors" columns show the
probabilistic errors in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies against the initialization by~\cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, e.g., only the back of a car is visible, we rely on 3D size priors). The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion.

From Table~\ref{tab:localizationExperiment}, the baseline method has the highest errors, which is likely due to lack of point tracks and incorrect point-to-object associations (using detection bounding boxes). Moreover, minimizing different combinations of energies yields lower errors than the initialization by~\cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization. Finally, we observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

>>>>

In this section, we benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation \cite{Brox_Malik_2010,Rao_etal_2010}. We then show how the proposed model may be applied for 3D object localization in road scenes. For our experiments, we use 35 sequences of the KITTI raw dataset~\cite{Geiger_etal_2012}, which are recorded under a variety of driving conditions and include 10,088 frames and 634 object tracks in total. 
%It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\begin{figure*}[!!t]
\centering
%\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
\includegraphics[width=0.95\textwidth]{graphics/figure5.png}
  \vspace{-0.3cm}
  \caption{\small Association errors on different sets of input point tracks. Numbers on the x-axis represent sequence numbers in the KITTI raw dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
  \vspace{-0.3cm}
  \label{fig:assoc-occ-results}
\end{figure*}

@@

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.090\textwidth}
\begin{figure*}[!!t]
  \centering
  \begin{tabular}{cc@{}c@{\hspace{0.1cm}}c@{}c@{}}
    & Associations & Errors & Associations & Errors\\
    \rotatebox{90}{\hspace{1em} RAS}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
	\rotatebox{90}{\hspace{1em} BM}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\    
    \rotatebox{90}{\hspace{1em} BBox}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{1em} Ours}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png}%
    & \includegraphics[height=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \vspace{-0.3cm}
  \caption{\small Qualitative results of the association experiment. The ``Associations" columns
  show the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. The ``Errors" columns show the
probabilistic errors in association: low error points are in blue while high error points are in red.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0 and 1 errors.}
\label{fig:qualitative}
\vspace{-0.3cm}
\end{figure*}

@@

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table \ref{tab:localizationExperiment}. The average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies against the initialization using \cite{Song_Chandraker_2014} and a simple baseline which fits a 3D cuboid on the 3D point cloud reconstructed using SFM within detection bounding boxes in consecutive frames (for unobservable dimensions, such as when only the back of a car is visible, we rely on 3D size priors). The energy $\EnergyTrackNoOcc$ represents the point track energy without accounting for occlusions, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the bounding box energy without the modification of $\bLambda_k$ that accounts for occlusion. We use $\lambda_{\text{track}} = 1$, $\lambda_{\text{detect}} = 1$, $\lambda_{\text{dyn}} = 10$, $\lambda_{\text{size}} = 7$. Please refer to the supplementary material for a detailed list of parameter settings.

From Table~\ref{tab:localizationExperiment}, the baseline method has the highest errors, which is likely due to lack of point tracks and incorrect point-to-object associations (using detection bounding boxes). Moreover, minimizing different combinations of energies yields lower errors than the initialization with \cite{Song_Chandraker_2014}, which shows the advantage of our energy minimization. Finally, we observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

### 2016-04-08 CVPR16/Source/intro.tex
Camera ready version

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Rao_etal_2010,Brox_Malik_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has been considered for multibody SFM \cite{Kundu_etal_2011}. However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

Another potential application of our proposed model is towards 3D localization in road scenes. Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either. In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs. Our model is continuous, so remains amenable to the use of continuous optimization tools.

>>>>

In particular, assigning 2D point tracks to independent, but potentially occluding, objects is a fundamental challenge in computer vision problems such as multibody SFM \cite{Ozden_etal_2010}. Recent works use motion segmentation \cite{Brox_Malik_2010,Rao_etal_2010} as a precursor to localizing objects, which often suffices for moving objects \cite{Tron_Vidal_2007} and has also been considered for multibody SFM \cite{Kundu_etal_2011}. However, motion-based segmentation is not always applicable in road scenes, due to static parked cars, or dynamic cars that move with similar velocities. Occlusions make the problem more severe since point tracks get clustered together for static objects and may frequently appear to change association among dynamic objects in 2D.
%In contrast, we leverage the success of 
Indeed, we show in Section \ref{sec:experiments} that our point track association outperforms state-of-the-art motion segmentation methods, as well as a baseline that uses detection bounding boxes but does not consider occlusions.

Another potential application of our proposed model is towards 3D localization in road scenes. Prior works such as \cite{Song_Chandraker_2015} combine information from point tracks and detection bounding boxes, but do not consider occlusions for either. In contrast, our unified occlusion model allows a probabilistic soft assignment of point tracks to objects, as well as an occlusion-aware interpretation of object detection outputs. Our model is continuous, so it remains amenable to the use of continuous optimization tools.

### 2016-04-08 CVPR16/Source/occlusion.tex
update Supp
Camera ready version

\begin{figure}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids, which leads to formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing face of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{figure}

\vspace{-0.3cm}
\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as
\begin{align}
  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
\end{align}
where $\cL(\cdot)$ is the logistic function given by
\begin{align}
  \cL(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
\end{align}
with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance. We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object. Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.

@@

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$. Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$. Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$ as
\begin{align}
   \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
\label{eq:evalPrefl}
\end{align}
The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, $\max$ ensures that negative probability due to gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero. $Z$ denotes the normalization factor. We note that in the extreme case of an object being fully opaque (i.e., $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection. Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.

@@

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability as follows
%
\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
\begin{align}
  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in the image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}}, \\
  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}.
\end{align}
%
In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and approximate formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively. Note that the choice of mean depth of the object causes some deviation from the exact transmission probability. However, the shift of transmission probability anywhere through the object is still a reasonable approximation as occluded points can only lie outside the object. On the other hand, it yields significant computational savings since ray intersections with an ellipsoid are expensive to evaluate densely.

>>>>

\begin{figure}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids, which leads to the formulation of transmission and reflection probabilities. This figure shows the reflection probability for the first object (in violet), which has high values around the camera-facing side of the object. Also, note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{figure}

\vspace{-0.3cm}
\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque and regions more likely to be free space considered more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whose opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at 3D location $\bx$ corresponding to an object $O_i$ centered at $\bp_i$ as
\begin{align}
  f^i_{\text{occ}}(\bx) = \cL(\bx; \bp_i, \bSigma_i),
\end{align}
where $\cL(\cdot)$ is the logistic function given by
\begin{align}
  \cL(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
\end{align}
with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma^{-1}(\bx-\bp)$ being the Mahalanobis distance. We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\bSigma_i$, depends on the dimensions of the object. Please refer to the supplementary material for the computation of $\bSigma_i$ from object dimensions.

@@

\vspace{-0.3cm}
\paragraph{Reflection probability}
Consider a 3D point $\bx_j$ observed in the image at pixel $\bu_j$. Let $\bK$ be the intrinsic calibration matrix for the camera and $\ray = \displaystyle\frac{\bK^{-1}\bu_j}{\lVert \bK^{-1}\bu_j \rVert}$ be the unit vector along the backprojected ray from the camera center passing through $\bu_j$. Then, the probability of reflection at depth $\lambda$ along the ray $\ray$, by an object $O_i$, is determined by the gradient of the object's occupancy function $f_{occ}^i$ as
\begin{align}
   \Prefl = \frac{1}{Z}(\max \{0, \nabla {f^i_{occ}}(\bx_j)^\top \ray \})^2.
\label{eq:evalPrefl}
\end{align}
The gradient $\nabla {f^i_{occ}}(\bx_j)$ encourages the reflection probability to be high near object boundaries, the $\max$ ensures that negative probability due to the gradient in the direction opposite to the ray is clipped off and squaring allows the function to be smooth near zero. Here, $Z$ denotes the normalization factor. We note that in the extreme case of an object being fully opaque (that is, $\nabla {f^i_{occ}(\bx_j)} \in \{0,1\}$), the above model reverts to a (squared) Lambertian reflection. Figure~\ref{fig:reflectiontransimission} shows an example of the reflection probability.

@@

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability, as follows:
%
\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
\begin{align}
  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i) \cL_{\lambda}(\lambda; \meandepth{i})),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in the image domain, with $\bmu_i$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain, with $\meandepth{i}$ being the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}}, \\
  \cL_{\lambda}(\lambda; \meandepth{i}) &= \frac{1}{1 + e^{-k_d(\lambda - \meandepth{i})}}.
\end{align}
%
In Figure \ref{fig:compare:exact:approx:ptrans}, we compare the exact and approximate formulations of transmission probability given by \eqref{eq:ptrans-integral} and \eqref{eq:evalCumulativePtrans}, respectively. Note that the choice of mean depth of the object causes some deviation from the exact transmission probability. However, the shift of transmission probability anywhere through the object is still a reasonable approximation as occluded points can only lie outside the object. On the other hand, it yields significant computational savings since ray intersections with an ellipsoid are expensive to evaluate densely.
